Dependently Typed Multi-stage Calculus

### 2019-11-20 slides/main.tex
Finished until page6.

% Remove all navigation symbols
\setbeamertemplate{navigation symbols}{}
% using non standard fonts for beamer
\usefonttheme{professionalfonts}
% Set the font size of titles
% See other font category at
% https://tex.stackexchange.com/questions/183052/what-are-all-the-possible-first-arguments-to-setbeamerfont
\setbeamerfont{title}{size=\normalsize}
\setbeamerfont{frametitle}{size=\normalsize}
\setbeamerfont{normal text}{size=\small}
\setbeamerfont{itemize/enumerate body}{size=\footnotesize}
\setbeamerfont{itemize/enumerate subbody}{size=\footnotesize}
\setbeamerfont{frametitle continuation}{size=\small}
\setbeamerfont{framesubtitle}{size=\small}
\setbeamerfont{abstract}{size=\small}
\setbeamerfont{projected text}{size=\small}
\setbeamerfont{block title}{size=\small}
\setbeamerfont{footline}{size=\tiny}

@@

\begin{frame}[fragile]{Application of Multi-stage Programming: vadd-gen}
    Generate efficient vector addition functions for given length vectors.
    \begin{verbatim}
 val vadd-gen : Int -> (Vec -> Vec -> Vec) code
 let vadd3 = vadd-gen 3;;
 val vadd : (Vec -> Vec -> Vec) code
 (run vadd3) [1;2;3] [4;5;6];;
  - : Vec = [5;7;9]
    \end{verbatim}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{The problem of vadd3 generated by vadd-gen}
    Runtime error occurs for wrong length vectors.
    \renewcommand{\V}{\text{Vec}}
    \begin{tabbing}
        \( \text{vadd3}\ [1;2;3;4]\ [4;5;6;7];; \) \\
        \( \longrightarrow \textbf{RUNTIME ERROR!} \)
    \end{tabbing}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Dependent Types}
    Types dependent on values
    \begin{itemize}
            \item Can give more fine restriction on terms.
    \end{itemize}
    \renewcommand{\V}{\text{Vec}\ }
    \begin{tabbing}
        \( [1;2;3]:\ (\V 3) \) \\
        \( [1;2;3;4]:\ (\V 4) \) \\
        \( \text{vadd3}:\ (\V 3) \to (\V 3) \to (\V 3) \)
    \end{tabbing}

    \note{
        By the way, we can write types dependent on values using dependent types.
    }
\end{frame}

@@

\begin{frame}[fragile]{Generated functions by vadd-gen in \LMD}
    Type system prevents illegal use of generated function.
    \renewcommand{\V}{\text{Vec}}
    \begin{tabbing}
        \( \text{vadd3}\ [1;2;3]\ [4;5;6];; \) \\
        \( - : \V = [5;7;9] \) \\[2mm]
        \( \text{vadd3}\ [1;2;3;4]\ [4;5;6;7];; \) \\
        \( \longrightarrow \textbf{TYPE ERROR!} \text{ (not RUNTIME ERROR)} \)
    \end{tabbing}
    \note{
        Type of generated functions by vadd-gen in \LMD have the length information in their types.
    }
\end{frame}

>>>>

% Remove all navigation symbols
\setbeamertemplate{navigation symbols}{}
% using non standard fonts for beamer
\usefonttheme{professionalfonts}
% Set the font size of titles
% See other font category at
% https://tex.stackexchange.com/questions/183052/what-are-all-the-possible-first-arguments-to-setbeamerfont
\setbeamerfont{title}{size=\normalsize}
\setbeamerfont{frametitle}{size=\normalsize}
\setbeamerfont{normal text}{size=\small}
\setbeamerfont{itemize/enumerate body}{size=\small}
\setbeamerfont{itemize/enumerate subbody}{size=\footnotesize}
\setbeamerfont{frametitle continuation}{size=\small}
\setbeamerfont{framesubtitle}{size=\small}
\setbeamerfont{abstract}{size=\small}
\setbeamerfont{projected text}{size=\small}
\setbeamerfont{block title}{size=\small}
\setbeamerfont{footline}{size=\tiny}

@@

\begin{frame}[fragile]{Application of Multi-stage Programming: vadd-gen}
    Generate efficient vector addition functions for given length.

    \begin{verbatim}
 val vadd-gen : Int -> (Vec -> Vec -> Vec) code
 # let vadd3 = vadd-gen 3;;
 (* vadd3 v w =                             *)
 (*   let (v, w)=(.~v, ,~w) in              *)
 (*   .< [v[0]+w[0];v[1]+w[1];v[2]+w[2]] >. *)
 val vadd3 : (Vec -> Vec -> Vec) code
 # (run vadd3) [1;2;3] [4;5;6];;
  - : Vec = [5;7;9]
    \end{verbatim}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{The problem of vadd3 generated by vadd-gen}
    Runtime error occurs for wrong length vectors.
    \begin{verbatim}
    # (run vadd3) [1;2] [4;5];;
    Exception: Failure
    \end{verbatim}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Dependent Types}
    \renewcommand{\V}{\text{Vec}\ }
    Types dependent on values
    \begin{itemize}
        \item Can prevents illegal use of {\verb|vadd3|}.
    \end{itemize}
 \begin{verbatim}
 - : [1;2]: Vec 2
 - : vadd3 : (Vec 3 -> Vec 3 -> Vec 3) code

 # (run vadd3) [1;2] [4;5];;
 [1;2] has type Vec 2
 but was expected of type Vec 3
 \end{verbatim}
    \note{
        By the way, we can write types dependent on values using dependent types.
    }
\end{frame}

% \begin{frame}[fragile]{Generated functions by vadd-gen in \LMD}
%     Type system prevents illegal use of generated function.
%     \renewcommand{\V}{\text{Vec}}
%     \begin{tabbing}
%         \( \text{vadd3}\ [1;2;3]\ [4;5;6];; \) \\
%         \( - : \V = [5;7;9] \) \\[2mm]
%         \( \text{vadd3}\ [1;2;3;4]\ [4;5;6;7];; \) \\
%         \( \longrightarrow \textbf{TYPE ERROR!} \text{ (not RUNTIME ERROR)} \)
%     \end{tabbing}
%     \note{
%         Type of generated functions by vadd-gen in \LMD have the length information in their types.
%     }
% \end{frame}

@@
